Expanding the scope of experimental archaeology using the Perception-Process-Product conceptual framework

### 2023-07-01 manuscript/manuscript.Rmd
minor updates.

In the past decades, actualistic experiments becomes more common [@liu2022]. Variability as revealed in experiment is crucial and cannot be simply replaced by ethnographic records because the many paleolithic technological components are not displayed in contemporary non-industrial societies, which usually feature technological systems with ground stone artifacts as the target products [e.g., @stout2002; @arthur2018]. Statistical techniques for developing causal inference from observational data has also been greatly boosted in recent years [@cunningham2021; @hernan2023]. It also echoes the recent calls for moving beyond the by providing detailed contextual information of the experiment [@holleman2020].

@@

>>>>

In the past decades, actualistic experiments becomes more common [@liu2022]. Variability as revealed in experiment is crucial and cannot be simply replaced by ethnographic records because the many paleolithic technological components are not displayed in contemporary non-industrial societies, which usually feature technological systems with ground stone artifacts as the target products [e.g., @stout2002; @arthur2018]. Statistical techniques for developing causal inference from observational data has also been greatly boosted in recent years [@cunningham2021; @hernan2023]. It also echoes the recent calls for moving beyond the by providing detailed contextual information of the experiment [@holleman2020]. how decontexualized law-like statements interact in a particular context.

@@

Again, actualistic expeirment as a huestric for hypothesis generation as well as a low-cost , echoing the spirit stated by Lin et al. [-@lin2018: 680-681] as well as Ingersoll and MacDonald [-@ingersoll1977] arguing that the the interaction between actualistic and controlled experiment "operates in a cyclical form of induction and deduction" [].
